Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-06 paper/paper.tex
pass on RQs

We mentioned above that http rules often used content options, which
associate with the message payload. For non-http rules, options are
often associated with packet fields. Let us consider a rule for an
ICMP attack as example. Figure~\ref{fig:icmp-packet-layout} shows the
layout of an ICMP packet. The packet fields ``Flags'' and ``Time to
Live'', declared in the IP header, are mapped to the \suri\ options
\CodeIn{flagbits} and \CodeIn{ttl}, respectively. Likewise, the fields
``Type'' and ``Code'', declared in the ICMP header, are mapped to the
options \CodeIn{itype} and \CodeIn{icode}, respectively. The values of
the options ``ttl'', ``itype'', and ``icode'' are the same as the
value of the corresponding fields in the ICMP packet. For the field
``Flags'' the value of the corresponding option is encoded in a
bitvector. For example, if the ``Flags'' field stores the value 1010,
the corresponding rule option will be \CodeIn{flagbits:RM}, as each
position of the vector encodes a different character in the
\CodeIn{flagbits} rule option. In summary, the value of several
options can be determined through transformation functions, as those
informally described above. One exception to this is the option
\CodeIn{threshold}, which is typically used in denial-of-service
attacks. That option operates over sequence of messages as opposed to
a single message. Consequently, it is not possible to determine its
values from a single message.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.27]{figs/ICMP-packet-structure.png}
\vspace{-2ex}
\caption{Layout of an ICMP packet.}
\vspace{-2ex}
\label{fig:icmp-packet-layout}
\end{figure}
%\vspace{-2ex}

@@

\setlength{\tabcolsep}{5pt}
\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks. Non-http attacks
    appear at the top; http attacks appear at the bottom.}
  \centering
  \begin{tabular}{llllp{8cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule
    Black Nurse & \cite{pcap-attacks} & DoS & ICMP & \textbf{icode}:3; \textbf{itype}:3; \textbf{threshold}: type both, track by\_dst, count 250, seconds 1;\\    
    Ping Scan & \cite{netmap} & AREC & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & \cite{hping3} & DoS & TCP & \textbf{flags}: S,12;
    \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5;\\
    UDP Teardrop & \Fix{WireShark} & DoS & UDP & \textbf{fragbits}:M; \textbf{id}:124; \\
    %%UDP Flood & MazeBolt & DoS & UDP & \textbf{fragbits}:M; \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5; \\
    \midrule
    %%Apache Struts 2 & \cite{wrccdc} & RCE & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    WeBid LFI \MyComment{Local File Inclusion} & \cite{nikto} & LFI & HTTP & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    %%WordPress Login & \cite{wrccdc} & PVE & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Basebuilder LFI & \cite{nikto} & LFI & HTTP & \textbf{content}:"GET"; http\_method; \textbf{content}:"/main.inc.php?"; nocase; http\_uri; \textbf{content}:"mj\_config[src\_path]="; nocase; http\_uri; \\
    Tomcat server snoop access & \cite{nikto} & AREC & HTTP & \textbf{content}:"/jsp/snp/"; http\_uri; \textbf{content}:".snp"; http\_uri;\\  
    \bottomrule
  \end{tabular}
\end{table*}

@@

\setlength{\tabcolsep}{2pt}
\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Vars.}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 34 & 3\\
    iisadmin access & 3 & 17 & 408 & 1 \\        
    JBoss JMX & 5 & 23 & 228 & 45 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid LFI & 1 & 23 & 11100 & 10\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 2 \\
    /system32/ in URI & 4 & 20 & 1,913 & 4 \\
    Basebuilder LFI & 1 & 22 & 18133 & 34 \\
    Tomcat Snoop Access & 1 & 24 & 29830 & 32 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

%% Note from Figure~\ref{fig:overview} that the positive traffic is an
%% input to the technique. The negative non-malicious traffic, however,
%% is not.

%subsection{Methodology}

%% \Gui{
%% O procedimento que já tínhamos representa a etapa de treinamento. Toda aquela parte que foi explicada na apresentação para os outros professores e descrito no paper. Descreverei novamente pra confirmar, e também foi adicionado uma pequena etapa.

%% TREINAMENTO

%% ->Syrius recebe como input um pcap contendo o ataque (no caso de ataques com content, usamos ataques do Nikto), um pcap benígno (usamos o bigflows.pcap) e um pcap contendo as variações de ataque (isso pode ser otimizado unificando com o pcap de ataque, mas por agora está assim)
%% ->É gerado a regra máxima através do tokenizer e engenharia reversa.
%% ->Syrius remove UM content de uma regra da lista de regras atuais (inicialmente apenas a regra máxima) e checa se a regra criada já existe na lista. Se não, a regra é adicionada à lista de regras-não-testadas. Syrius faz isso duas vezes por regra, para todas as regras da lista.
%% ->A lista de regras-não-testadas é inicializada no suricata e então o rodamos com o pcap benígno de treinamento (75porcento do total). Verificando no arquivo de log do suricata, caso a regra alerte, ela é removida da lista. As regras restantes vão para a lista de regras atuais.
%% ->Quando não houver alterações, retornamos a lista com todas as regras que deram certo.
%% ->Opcionalmente, ainda rodamos no final uma variação de ataque (no momento apenas um pacote devido ao número limitado que temos do ataque). Ao contrário do método com pacotes benígnos, se a regra NÃO alertar, ela é removida.
%% ->Calculamos o fitness de cada regra e ordenamos de acordo com o fitness resultante. Esta lista ordenada é o fim do treinamento.

%% TESTE

%% ->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap benígno de teste (25porcento restantes) para cálculo do precision. O cálculo ficou basicamente, por regra: [100 - (numero-de-alertas/total-de-pacotes)]

%% ->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap com variações de ataque (caso a etapa opcional ocorrer, não usamos aquele pacote especifico) para cálculo do recall. O cálculo ficou basicamente, por regra: [(100/total-de-pacotes) * n-alertas].

%% ->Por final calculamos o F1 Score por regra: [2*((precision*recall)/(precision+recall))]

%% ->O teste retorna um csv contendo a lista de regras ordenadas com seus respectivos precision, recall e f1 score.
%% }

%% \Gui{We are using the bigflows.pcap provided by tcpreplay on http://tcpreplay.appneta.com/wiki/captures.html "This is a capture of real network traffic on a busy private network’s access point to the Internet"
%%  }

%% \Luc{entrada: utilizamos a ferramenta hping3 para executar o ataque em um alvo arbitrario dentro da rede (n ha necessidade de haver um alvo real para executar o hping3) e capturamos o trafego gerado com o wireshark. o comando utilizado foi:\\*
%% \texttt{\# hping3 -d 80 -w 64 -S -p 80 --flood --rand-source 192.138.1.115} \\*
%% que envia pacotes de 80 bytes (-d 80), com a flag SYN habilitada (-S), tamanho de janela de 64 bytes (-w 64), direcionados a porta 80 (-p 80). A flag --flood indica q o hping3 vai enviar os pacotes o mais rápido possível. a flag --rand-source indica que cada pacote vai ter um ip de origem aleatorio. 192.138.1.115 é o alvo.\\*
%% O trafego armazenado contem 40 mil pacotes SYN, enviados no intervalo de 1 segundo,  pegamos uma amostra de 20 desses pacotes para representar o flood e servir como entrada.\\*
%% O wireshark armazena os pacotes no formato pcap, utilizamos a ferramenta tcpreplay para reproduzir o trafego com o comando:\\*
%% \texttt{\# tcpreplay --pps 200 --intf1=wlp2s0 Datasets/syn-flood-sample.pcap}\\*
%% Nesse caso, estamos enviando os pacotes armazenados em \texttt{Datasets/syn-flood-sample.pcap} a uma taxa de 200 pacotes por segundo (\texttt{-pps 200}) utilizando a interface wlp2s0 (\texttt{--intf1 wlp2s0})\\* 
%% Há diferenças entre os pacotes na opção ack.\\* 
%% Por que 20? Apenas para gerar a regra mais rapidamente, poderia ser qualquer valor maior ou menor. No final, o parâmetro \texttt{count} da opção \texttt{threshold} vai ser alterado pelo adm da rede.\\*
%% Intervalo de reprodução: 0.005 segundo

%% }

%% \Fix{any other detail we should consider?}

@@

This section reports on the performance evaluation of \tname. The
evaluation metric used is the position of the golden rule at the
ranked list of plausible rules produced by the tool implementing the
technique (see Figure~\ref{fig:overview}). This metric is a proxy of
human performance in analyzing the list of plausible rules that
capture only the malicious traffic provided on input.

Table~\ref{table:results} shows results. Column ``Name'' shows the
name of the attack, column ``\#~Vars.'' shows the number of variants
of the attack, column ``\#~Option Cand. (step 1)'' shows the number of
option candidates reported by \tname\ at step 1, column ``\#~Plausible
Rules (step 2)'' shows the number of plausible rules reported by
\tname\ at step 2, column ``Rank (step 3)'' shows the position of the
golden rule in the ranked list reported at step 3 of the technique.
It is worth to indicate that column ``\#~Vars.'' shows the input of
\tname\ that varies across different attacks. Although \tname\ also
depends on the data sets of benign traffic and existing \suri\ rules,
these inputs are constant across different executions of the tool. The
rest of the columns show the progress of the tool at various stages
and provide an indication of complexity of the synthesis problem.

@@

\newcommand{\percTopFiveRanking}{\Fix{X\%}}

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top five rules of the ranking in
\percTopFiveRanking\ of the cases. It is important to note that the
number of options in the ground truth (Table~\ref{table:attacks},
column ``Ground Truth'') is not an indication of difficulty to
synthesize rules. Note that in \Fix{most?} of the cases where the
ground truth rule contains only one content options the number of
option candidates and plausible rules produced is high.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.4,trim=20 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.4,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}
    \caption{scripttag}    
  \end{subfigure}%
\caption{Impact of number of positive examples.}
\label{fig:impact-number-attacks}
\end{figure}

@@

The SYN Flood attack is a denial-of-service attack that exploits a vulnerability in the TCP/IP handshake
to establish a TCP connection~\cite{cloudfare-synflood}. The handshake
works as follows in normal circumstances. First, a client sends a SYN
packet to the server, requesting a connection. Second, the server
responds with a SYN-ACK packet to the client. Third, the client
responds with an ACK message and the connection is established. Aware
of the protocol, an attacker sends multiple SYN packets to different
ports of a server, often using fake IP addresses. Then, after the
server responds with a SYN-ACK packet, the client keeps sending other
SYN packets to avoid the connection to time out. Without proper
protection, the server accepts these malicious requests and eventually
legitimate requests cannot be satisfied due to resource exhaustion.

@@

Figure~\ref{fig:synflood-example} shows a Suricata rule that captures
this attack. This rule was obtained from the Emerging Threats Open
Ruleset~\cite{emerging-threats-open}. The relevant options in the
rule appear in bold---the option \CodeIn{flags: S,12}, identifies a
SYN packet in a TCP packet and the option \CodeIn{threshold: type
  both, track by\_dst, count 5000, seconds 5} indicates that a high
volume of such packets should be requested in a short period of
time. The other options are for documentation purposes.

>>>>

We mentioned above that http rules often used content options, which
associate with the message payload. For non-http rules, options are
often associated with packet fields. Let us consider a rule for an
icmp attack as example. Figure~\ref{fig:icmp-packet-layout} shows the
layout of an icmp packet. The packet fields ``Flags'' and ``Time to
Live'', declared in the ip header, are mapped to the \suri\ options
\CodeIn{flagbits} and \CodeIn{ttl}, respectively. Likewise, the fields
``Type'' and ``Code'', declared in the icmp header, are mapped to the
options \CodeIn{itype} and \CodeIn{icode}, respectively. The values of
the options ``ttl'', ``itype'', and ``icode'' are the same as the
value of the corresponding fields in the icmp packet. For the field
``Flags'' the value of the corresponding option is encoded in a
bitvector. For example, if the ``Flags'' field stores the value 1010,
the corresponding rule option will be \CodeIn{flagbits:RM}, as each
position of the vector encodes a different character in the
\CodeIn{flagbits} rule option. In summary, the value of several
options can be determined through transformation functions, as those
informally described above. One exception to this is the option
\CodeIn{threshold}, which is typically used in denial-of-service
attacks. That option operates over sequence of messages as opposed to
a single message. Consequently, it is not possible to determine its
values from a single message.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.27]{figs/ICMP-packet-structure.png}
\vspace{-2ex}
\caption{Layout of an icmp packet.}
\vspace{-2ex}
\label{fig:icmp-packet-layout}
\end{figure}
%\vspace{-2ex}

@@

%\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{0.9}
\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks. Non-http attacks
    appear at the top; http attacks appear at the bottom.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lcccp{10cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule
    Black Nurse & \cite{pcap-attacks} & DoS & icmp & \textbf{icode}:3; \textbf{itype}:3; \textbf{threshold}: type both, track by\_dst, count 250, seconds 1;\\    
    Ping Scan & \cite{netmap} & AREC & icmp & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & \cite{hping3} & DoS & tcp & \textbf{flags}: S,12;
    \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5;\\
    UDP Teardrop & \cite{udp-teardrop-source} & DoS & udp & \textbf{fragbits}:M; \textbf{id}:124; \\
    %%UDP Flood & MazeBolt & DoS & UDP & \textbf{fragbits}:M; \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5; \\
    \midrule
    %%Apache Struts 2 & \cite{wrccdc} & RCE & http & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & http \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & http \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    WeBid LFI \MyComment{Local File Inclusion} & \cite{nikto} & LFI & http & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    %%WordPress Login & \cite{wrccdc} & PVE & http & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Basebuilder LFI & \cite{nikto} & LFI & http & \textbf{content}:"GET"; http\_method; \textbf{content}:"/main.inc.php?"; nocase; http\_uri; \textbf{content}:"mj\_config[src\_path]="; nocase; http\_uri; \\
    Tomcat server snoop access & \cite{nikto} & AREC & http & \textbf{content}:"/jsp/snp/"; http\_uri; \textbf{content}:".snp"; http\_uri;\\  
    \bottomrule
  \end{tabular}
\end{table*}

@@

\renewcommand{\arraystretch}{0.9}
\setlength{\tabcolsep}{2pt}
\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Vars.}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 34 & 3\\
    iisadmin access & 3 & 17 & 408 & 1 \\        
    JBoss JMX & 5 & 23 & 228 & 45 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid LFI & 1 & 23 & 11,100 & 10\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 2 \\
    /system32/ in URI & 4 & 20 & 1,913 & 4 \\
    Basebuilder LFI & 1 & 22 & 18,133 & 34 \\
    Tomcat Snoop Access & 1 & 24 & 29,830 & 32 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

@@

RQ1 addresses the performance of \tname. The metric we use is the
position of the golden rule at the ranked list of plausible rules
reported by \tname\ (see Figure~\ref{fig:overview}). This metric is a
proxy of human performance in analyzing the list of plausible rules.

Table~\ref{table:results} shows results. Column ``Name'' shows the
name of the attack, column ``\#~Vars.'' shows the number of variants
of the attack, column ``\#~Option Cand. (step 1)'' shows the number of
option candidates reported by \tname\ at step 1, column ``\#~Plausible
Rules (step 2)'' shows the number of plausible rules reported by
\tname\ at step 2, and column ``Rank (step 3)'' shows the position of the
golden rule in the ranked list reported at step 3.
It is important to indicate that column ``\#~Vars.'' shows the input of
\tname\ that varies across different attacks. Although \tname\ also
depends on the data sets of benign traffic and existing \suri\ rules,
these inputs are constant across different executions of the tool. The
rest of the columns show the progress of the tool at various stages
and provide an indication of complexity of the synthesis problem.

@@

\newcommand{\percTopFiveRanking}{66.7\% (=10/15)}

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top five rules of the ranking in
\percTopFiveRanking\ of the cases.

%% It is important to note that the
%% number of options in the ground truth (Table~\ref{table:attacks},
%% column ``Ground Truth'') is not an indication of difficulty to
%% synthesize rules. In facto, note that in  of the cases where the
%% ground truth rule contains only one content options the number of
%% option candidates and plausible rules produced is high.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.4,trim=20 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.4,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}
    \caption{scripttag}    
  \end{subfigure}%
\vspace{-2ex}  
\caption{Impact of number of positive examples.}
\label{fig:impact-number-attacks}
\vspace{-2ex}
\end{figure}

@@

The SYN Flood attack is a denial-of-service attack that exploits a
vulnerability in the tcp/ip handshake
to establish a tcp connection~\cite{cloudfare-synflood}. The handshake
works as follows in normal circumstances. First, a client sends a SYN
packet to the server, requesting a connection. Second, the server
responds with a SYN-ACK packet to the client. Third, the client
responds with an ACK message and the connection is established. Aware
of the protocol, an attacker sends multiple SYN packets to different
ports of a server, often using fake IP addresses. Then, after the
server responds with a SYN-ACK packet, the client keeps sending other
SYN packets to avoid the connection to time out. Without proper
protection, the server accepts these malicious requests and eventually
legitimate requests cannot be satisfied due to resource exhaustion.

@@

Figure~\ref{fig:synflood-example} shows a Suricata rule that captures
this attack. This rule was obtained from the Emerging Threats Open
Ruleset~\cite{emerging-threats-open}. The relevant options in the
rule appear in bold---the option \CodeIn{flags: S,12}, identifies a
SYN packet in a tcp packet and the option \CodeIn{threshold: type
  both, track by\_dst, count 5000, seconds 5} indicates that a high
volume of such packets should be requested in a short period of
time. The other options are for documentation purposes.
